flowCore: data structures for flow cytometry data

### 2007-03-16 inst/doc/HowTo-flowCore.Rnw
Doc updates and a couple of minor bug fixes (like adding the '!' back into complement filters...)
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@23212 bc3139a8-67e5-0310-9ffc-ced21a209358
fix definition of generic methods fix definition of filterCollection, can not extend environment
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@23255 bc3139a8-67e5-0310-9ffc-ced21a209358

\section{Introduction}
Traditionnally, flow cytometry has been a tube-based technique limited to small-scale laboratory and clinical studies. 
High throughput methods for flow cytometry have recently been developed for drug discovery and advanced research methods 
\cite{Gasparetto2004, Young2004}. As an example, the flow cytometry high content screening (FC-HCS) can process up 
to a thousand samples daily at a single workstation, and the results have been equivalent or superior to traditional 
manual multiparameter staining and analysis techniques. \\

@@

\subsection{flowSet}
An flow cytometry experiment usually include several sample and several measurements. 
A data structure is thus needed to store those collections of measurements.  
The package \Rpackage{flowCore} stores the measurement and the associated data 
information in objects of class \Robject{flowSet}. 
A\Robject{flowSet} object contains two main slot exprs, an enviroment data astructure 
that stores the flow cytometry measurements and the phenoData. The phenoData slot 
contains all the relevant experiment-wide meta-data, \textit{e.g.} 
phenotypic and experimental information relevant to the management and/or the analysis of the data.\\

>>>>

\section{Introduction}
Traditionally, flow cytometry has been a tube-based technique limited to small-scale laboratory and clinical studies. 
High throughput methods for flow cytometry have recently been developed for drug discovery and advanced research methods 
\cite{Gasparetto2004, Young2004}. As an example, the flow cytometry high content screening (FC-HCS) can process up 
to a thousand samples daily at a single workstation, and the results have been equivalent or superior to traditional 
manual multiparameter staining and analysis techniques. \\

@@

\subsection{flowSet}
An flow cytometry experiment usually include several sample and several measurements. 
A data structure is thus needed to store those collections of measurements.  
The package \Rpackage{flowCore} stores the measurement and the associated data 
information in objects of class \Robject{flowSet}. 
A \Robject{flowSet} object contains two main slots \Robject{exprs}, an environment data structure 
that stores the flow cytometry measurements and the \Robject{phenoData}. The \Robject{phenoData} slot 
contains all the relevant experiment-wide meta-data, \textit{e.g.} 
phenotypic and experimental information relevant to the management and/or the analysis of the data.\\
